Supplements for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'

### 2023-05-16 stats/supplements_validity.Rmd
clean up data file and naming conventions. incorporate manuels feedback

socenv_predictordistributions
saveRDS(socenv_predictordistributions, file = "../saves/socenv_predictordistributions.rds")

@@

```{r socenv_savemodels}
write.csv(mSEnull, "../saves/mSEnull.csv", quote = F, row.names = F)
saveRDS(mSEnull, "../saves/mSEnull.rds")
write.csv(mSEccAge, "../saves/mSEccAge.csv", quote = F, row.names = F)
saveRDS(mSEccAge, "../saves/mSEccAge.rds")
write.csv(mSEccHours, "../saves/mSEccHours.csv", quote = F, row.names = F)
saveRDS(mSEccHours, "../saves/mSEccHours.rds")
write.csv(mSEhhTotal, "../saves/mSEhhTotal.csv", quote = F, row.names = F)
saveRDS(mSEhhTotal, "../saves/mSEhhTotal.rds")
write.csv(mSEhhSibs, "../saves/mSEhhSibs.csv", quote = F, row.names = F)
saveRDS(mSEhhSibs, "../saves/mSEhhSibs.rds")
write.csv(mSEsibsChildAged, "../saves/mSEsibsChildAged.csv", quote = F, row.names = F)
saveRDS(mSEsibsChildAged, "../saves/mSEsibsChildAged.rds")
write.csv(mSEsiblingsVarietyScoreP, "../saves/mSEsiblingsVarietyScoreP.csv", quote = F, row.names = F)
saveRDS(mSEsiblingsVarietyScoreP, "../saves/mSEsiblingsVarietyScoreP.rds")
write.csv(mSEsiblingsVarietyScoreW, "../saves/mSEsiblingsVarietyScoreW.csv", quote = F, row.names = F)
saveRDS(mSEsiblingsVarietyScoreW, "../saves/mSEsiblingsVarietyScoreW.rds")
write.csv(mSEPE, "../saves/mSEPE.csv", quote = F, row.names = F)
saveRDS(mSEPE, "../saves/mSEPE.rds")
```

@@

```{r socenv_posteriordraws}
socenv_draws <- bind_rows(
  mSEccAge %>% gather_draws(b_ccAge),
  mSEccHours %>% gather_draws(b_ccHours), 
  mSEhhTotal %>% gather_draws(b_hhTotal), 
  mSEhhSibs %>% gather_draws(b_hhSibs), 
  mSEsibsChildAged %>% gather_draws(b_sibsChildAged), 
  mSEsiblingsVarietyScoreP %>% gather_draws(b_siblingsVarietyScoreP), 
  mSEsiblingsVarietyScoreW %>% gather_draws(b_siblingsVarietyScoreW),
  mSEPE %>% gather_draws(b_pe)
  ) %>% 
  mutate(
    predictor = factor(.variable, 
                       levels = c("b_hhSibs", 
                                  "b_siblingsVarietyScoreP", 
                                  "b_sibsChildAged", 
                                  "b_hhTotal", 
                                  "b_ccHours", 
                                  "b_ccAge", 
                                  "b_siblingsVarietyScoreW", 
                                  "b_pe"), 
                       labels = c("# Children in household aged 0-18", 
                                  "Sibling variety score (Peterson, 2000)", 
                                  "# Children in household aged 1-12", 
                                  "# Household members", 
                                  "Average hours spent in childcare per day", 
                                  "Age of childcare entry", 
                                  "Sibling variety score (Cassidy et al., 2005)", 
                                  "Peer exposure index")
                       )  
  ) %>% 
  rename(estimate = .value)

@@

```{r socenv_plot_winning}
socenv_plot_winning <- socenv_draws %>% 
  filter(predictor == "Age of childcare entry") %>% 
  ggplot(., aes(y = predictor, x = estimate)) +
  tidybayes::stat_halfeye(.width = c(.95, .8), scale = 0.8, slab_color = "#006c66", slab_fill = "#EBECEC", slab_alpha = 0.9) +
  labs(x = "Posterior estimate when predicting TANGO score", y = "") +
  guides(fill = "none")+
  geom_vline(xintercept = 0, linetype = "dashed") +
  coord_cartesian(expand = TRUE, ylim = c(1.5, 1.5)) +
  theme_classic()

socenv_plot_winning

saveRDS(socenv_plot_winning, file = "../saves/socenv_plot_winning.rds")
# ggsave("../figures/socenv_plot_winning.png", width = 10, height = 6, scale = 1, bg = "white")
```

```{r socenv_plot_allother}
socenv_plot_allother <- socenv_draws %>% 
  filter(predictor != "Age of childcare entry") %>% 
  ggplot(., aes(y = predictor, x = estimate)) +
  tidybayes::stat_halfeye(.width = c(.95, .8), scale = 1, slab_color = "#006c66", slab_size = 0.5, slab_fill = "#EBECEC", slab_alpha = 0.9) +
  labs(x = "Posterior estimate when predicting TANGO score", y = "") +
  guides(fill = "none")+
  geom_vline(xintercept = 0, linetype = "dashed") +
  coord_cartesian(expand = TRUE, ylim = c(1.5, 7.5)) +
  theme_classic()

socenv_plot_allother

saveRDS(socenv_plot_allother, file = "../saves/socenv_plot_allother.rds")
# ggsave("../figures/socenv_plot_allother.png", width = 10, height = 6, scale = 1, bg = "white")
```

@@

vali_sample
saveRDS(vali_sample, file = "../saves/vali_sample.rds")
```

@@

```{r orev_modelplot}
orev_modelplot <- orev_draws %>% 
  ggplot(., aes(x = estimate, y = predictor)) +
 tidybayes::stat_halfeye(.width = c(.95, .8), scale = 1, slab_color = "#006c66", slab_fill = "#EBECEC", slab_alpha = 0.9) +
    labs(x = "Posterior estimate when predicting oREV score", y = "") +
  guides(fill = "none")+
  geom_vline(xintercept = 0, linetype = "dashed") +
  coord_cartesian(expand = TRUE, xlim = c(-0.1, 0.6), ylim = c(1.5, 2.5)) +
  theme_classic()

@@

  labs(x = "TANGO score", y = "oREV score", col = "Age in years") + 
  scale_x_continuous(limits = c(0, 1.05), breaks = seq(0, 1, 0.25)) + 
  scale_y_continuous(limits = c(0, 1.1), breaks = seq(0, 1, 0.25)) +

  theme(legend.title = element_text(size = 9), 
        legend.key.size = unit(0.4, "cm"), 
        legend.direction = "vertical", 
        legend.box = "horizontal",
        legend.position = c(0.2, 0.18), 
        legend.background = element_blank(),
        legend.box.background = element_rect(colour = "black"), 
        legend.text = element_markdown()
        )

@@

```{r arrange_plots}
vali_arrangedplot <- ggarrange(
  ggarrange(
    socenv_plot_winning,
    socenv_plot_allother,
    ncol = 2,
    labels = c("A", "B")
  ),

  ggarrange(
    orev_modelplot, 
    orev_plot,
    ncol = 2,
    labels = c("C", "D")
  ), 
  nrow = 2
  )

vali_arrangedplot

saveRDS(vali_arrangedplot, file = "../saves/vali-arrangedplot.rds")
ggsave("../figures/tango_vali_arrangedplot.png", width = 8.5, height = 6, scale = 1.5, bg = "white")
```

@@

  labs(x = "TANGO score", y = "oREV score", col = "Age in years") + 
  scale_x_continuous(limits = c(0, 1.05), breaks = seq(0, 1, 0.5)) + 
  scale_y_continuous(limits = c(0, 1.1), breaks = seq(0, 1, 0.25)) +
  facet_grid(~ ageInYears) + 
  theme(legend.position = "none")
d
orev_agegroup

saveRDS(orev_agegroup, file = "../saves/tango_orev_byagegroup.rds")
ggsave("../figures/tango_supplements_orev_byagegroup.png", width = 7, height = 4)
```

>>>>

socenv_predictordistributions
saveRDS(socenv_predictordistributions, file = "../saves/socenv_predictordistributions.rds")
write.csv(socenv_predictordistributions, "../saves/socenv_predictordistributions.csv", quote = F, row.names = F)

@@

```{r socenv_savemodels}
saveRDS(mSEnull, "../saves/mSEnull.rds")
saveRDS(mSEccAge, "../saves/mSEccAge.rds")
saveRDS(mSEccHours, "../saves/mSEccHours.rds")
saveRDS(mSEhhTotal, "../saves/mSEhhTotal.rds")
saveRDS(mSEhhSibs, "../saves/mSEhhSibs.rds")
saveRDS(mSEsibsChildAged, "../saves/mSEsibsChildAged.rds")
saveRDS(mSEsiblingsVarietyScoreP, "../saves/mSEsiblingsVarietyScoreP.rds")
saveRDS(mSEsiblingsVarietyScoreW, "../saves/mSEsiblingsVarietyScoreW.rds")
saveRDS(mSEPE, "../saves/mSEPE.rds")
```

@@

```{r socenv_posteriordraws}
socenv_draws <- bind_rows(
  mSEccAge %>% gather_draws(b_ccAge),
  mSEccHours %>% gather_draws(b_ccHours), 
  mSEhhTotal %>% gather_draws(b_hhTotal), 
  mSEhhSibs %>% gather_draws(b_hhSibs), 
  mSEsibsChildAged %>% gather_draws(b_sibsChildAged), 
  mSEsiblingsVarietyScoreP %>% gather_draws(b_siblingsVarietyScoreP), 
  mSEsiblingsVarietyScoreW %>% gather_draws(b_siblingsVarietyScoreW),
  mSEPE %>% gather_draws(b_pe)
  ) %>% 
  mutate(
    predictor = factor(.variable, 
                       levels = c(
                                  "b_ccAge", 
                                  "b_hhSibs", 
                                  "b_pe",
                                  "b_sibsChildAged", 
                                  "b_siblingsVarietyScoreW", 
                                  "b_siblingsVarietyScoreP", 
                                  "b_hhTotal", 
                                  "b_ccHours"
                                  ), 
                       labels = c(
                                  "Age of childcare entry", 
                                  "# Children in household aged 0-18", 
                                  "Peer exposure index",
                                  "# Children in household aged 1-12", 
                                  "Sibling variety score (Cassidy et al., 2005)", 
                                  "Sibling variety score (Peterson, 2000)", 
                                  "# Household members", 
                                  "Average hours spent in childcare per day" 
                                  )
                       )  
  ) %>% 
  rename(estimate = .value)

@@

```{r socenv_plot}
socenv_plot <- socenv_draws %>% 
  mutate(
    winning_model = ifelse(predictor == "Age of childcare entry", TRUE, FALSE)
  ) %>% 
  ggplot(., aes(x = estimate, y = reorder(predictor, desc(predictor)), fill = winning_model)) +
  tidybayes::stat_halfeye(.width = c(.95, .8), scale = 0.8, slab_color = "#006c66", slab_size = 0.5, slab_alpha = 0.4) +
  scale_fill_manual(values = c("#EBECEC", "#006c66")) +
  labs(x = "Posterior estimate when predicting TANGO score", y = "") +
  guides(fill = "none")+
  geom_vline(xintercept = 0, linetype = "dashed") +
  coord_cartesian(expand = TRUE, ylim = c(1.5, 8.5)) +
  theme_classic()

socenv_plot

saveRDS(socenv_plot, file = "../saves/socenv_plot.rds")
# ggsave("../figures/socenv_plot.png", width = 10, height = 6, scale = 1, bg = "white")
```

@@

vali_sample
saveRDS(vali_sample, file = "../saves/vali_sample.rds")
write.csv(vali_sample, "../saves/vali_sample.csv", quote = F, row.names = F)
```

@@

```{r orev_modelplot}
orev_modelplot <- orev_draws %>% 
  ggplot(., aes(x = estimate, y = predictor)) +
 tidybayes::stat_halfeye(.width = c(.95, .8), scale = 1, slab_color = "#006c66", slab_fill = "#006c66", slab_alpha = 0.4) +
    labs(x = "Posterior estimate when predicting oREV score", y = "") +
  guides(fill = "none")+
  geom_vline(xintercept = 0, linetype = "dashed") +
  coord_cartesian(expand = TRUE, xlim = c(-0.1, 0.6), ylim = c(1.5, 2.5)) +
  theme_classic()

@@

  labs(x = "TANGO score", y = "oREV score", col = "Age in years") + 
  scale_x_continuous(limits = c(0, 1.05), breaks = seq(0, 1, 0.25)) + 
  scale_y_continuous(limits = c(0, 1.05), breaks = seq(0, 1, 0.25)) +

  theme(legend.title = element_text(size = 9), 
        legend.key.size = unit(0.4, "cm"), 
        legend.direction = "vertical", 
        legend.box = "horizontal",
        legend.position = c(0.8, 0.18), 
        legend.background = element_blank(),
        legend.box.background = element_rect(colour = "black"), 
        legend.text = element_markdown()
        )

@@

```{r vali_plot}
ggarrange(
  socenv_plot,
  orev_modelplot, 
  orev_plot,
  ncol = 3, 
  widths = c(1.2, 1, 1),
  labels = c("A", "B", "C")
)

ggsave("../figures/tango_vali_plot.png", width = 8, height = 2, scale = 2, bg = "white")
ggsave("../figures/tango_vali_plot.pdf", width = 8, height = 2, scale = 2, bg = "white")
```

@@

  labs(x = "TANGO score", y = "oREV score", col = "Age in years") + 
  scale_x_continuous(limits = c(0, 1.05), breaks = seq(0, 1, 0.5)) + 
  scale_y_continuous(limits = c(0, 1.1), breaks = seq(0, 1, 0.25)) +
  facet_grid(~ ageInYears) + 
  theme(legend.position = "none")

orev_agegroup

saveRDS(orev_agegroup, file = "../saves/tango_orev_byagegroup.rds")
ggsave("../figures/tango_supplements_orev_byagegroup.png", width = 7, height = 4)
ggsave("../figures/tango_supplements_orev_byagegroup.pdf", width = 7, height = 4)
```

### 2023-05-16 stats/supplements_webcamcoding.Rmd
clean up data file and naming conventions. incorporate manuels feedback

```{r load_data}
webcam_data <- readRDS(file = "../data/tango-testtrials.rds") %>% 
  filter(studytype == "vali" & datacollection == "remote - unsupervised" & studyversion == "box" & webcam == TRUE & ageInYears == 3) %>% 
  group_by(subjID) %>% 
  # determine order of factors
  mutate(
    # for models, summarize targetPositions in a way that it's symmetrical for left/ right side
    # the smaller the value, the more central the position
    symmetricPosition = case_when(
                                  targetPosition == "box3" ~ 0, 
                                  targetPosition == "box2" | targetPosition == "box4" ~ 1,
                                  targetPosition == "box1" | targetPosition == "box5" ~ 2),
    targetPosition = factor(targetPosition, levels = c("box1", "box2", "box3", "box4", "box5")), 
    proportionCorrectBox = mean(correctBox, na.rm = TRUE),
  )
```

@@

write.csv(perTrial_draws, "../saves/supplements-webcamcoding-perTrialdraws.csv", quote = F, row.names = F)
saveRDS(perTrial_draws, "../saves/supplements-webcamcoding-perTrialdraws.rds")
```

@@

write.csv(perSubject_draws, "../saves/supplements-webcamcoding-perSubjectdraws.csv", quote = F, row.names = F)
saveRDS(perSubject_draws, "../saves/supplements-webcamcoding-perSubjectdraws.rds")
```

@@

ggsave("../figures/tango_supplements_webcamcoding.png", width = 10, height = 5, scale = 1, bg = "white")
```

@@

write.csv(overall_results, "../saves/supplements-webcamcoding-results.csv", quote = F, row.names = F)
saveRDS(overall_results, "../saves/supplements-webcamcoding-results.rds")
```

>>>>

```{r load_data}
webcam_data <- readRDS(file = "../data/tango-testtrials.rds") %>% 
  filter(studytype == "vali" & datacollection == "remote - unsupervised" & studyversion == "box" & !is.na(nrRepeatedTestquestion) & ageInYears == 3) %>% 
  group_by(subjID) %>% 
  # determine order of factors
  mutate(
    # for models, summarize targetPositions in a way that it's symmetrical for left/ right side
    # the smaller the value, the more central the position
    symmetricPosition = case_when(
                                  targetPosition == "box3" ~ 0, 
                                  targetPosition == "box2" | targetPosition == "box4" ~ 1,
                                  targetPosition == "box1" | targetPosition == "box5" ~ 2),
    targetPosition = factor(targetPosition, levels = c("box1", "box2", "box3", "box4", "box5")), 
    proportionCorrectBox = mean(correctBox, na.rm = TRUE),
  )
```

@@

write.csv(perTrial_draws, "../saves/supplements_webcamcoding_perTrialdraws.csv", quote = F, row.names = F)
saveRDS(perTrial_draws, "../saves/supplements_webcamcoding_perTrialdraws.rds")
```

@@

write.csv(perSubject_draws, "../saves/supplements_webcamcoding_perSubjectdraws.csv", quote = F, row.names = F)
saveRDS(perSubject_draws, "../saves/supplements_webcamcoding_perSubjectdraws.rds")
```

@@

ggsave("../figures/tango_supplements_webcamcoding.png", width = 10, height = 5, scale = 1, bg = "white")
ggsave("../figures/tango_supplements_webcamcoding.pdf", width = 10, height = 5, scale = 1, bg = "white")
```

@@

write.csv(overall_results, "../saves/supplements_webcamcoding_results.csv", quote = F, row.names = F)
saveRDS(overall_results, "../saves/supplements_webcamcoding_results.rds")
```

### 2023-05-16 supplements/supplements.Rmd
clean up data file and naming conventions. incorporate manuels feedback

---
title             : "Supplements for the manuscript  'TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'"
shorttitle        : "Supplements"
author:

  - name          : "Julia Prein"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
    email         : "julia_prein@eva.mpg.de"

  - name          : "Manuel Bohn"
    affiliation   : "1"
  - name          : "Steven Kalinke"
    affiliation   : "1"
  - name          : "Daniel B. M. Haun"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
floatsintext      : yes
bibliography      : ["../../references.bib"]
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---

@@

```{r sample}
testtrials <- readRDS(file = "../data/tango-testtrials.rds") %>% 
  # determine order of factors
  mutate(
    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
    studyversion = factor(studyversion, levels = c("hedge", "box")), 
    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
    sample = factor(sample, levels = c("kids", "adults")), 
    studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
  )
```

@@

```{r webcam_table}
webcam_models <- readRDS(file = "../saves/supplements-webcamcoding-results.rds") %>%
  mutate(across(c(WAIC, Weight, ELPD_DIFF, SE_ELPD_DIFF), as.numeric)) %>%
  mutate_if(is.numeric, round, 2)

@@

```{r adult_sample_country, include=FALSE}
levels(testtrials$`Current Country of Residence`)
```

```{r adult_sample_countryn, echo=FALSE}
adult_sample_countryn <- testtrials %>% 
  group_by(subjID) %>% 
  slice(1) %>% 
  group_by(`Current Country of Residence`, studytype) %>%
  summarise(n = n()) %>%
  arrange(studytype, -n) %>% 
  filter(!is.na(`Current Country of Residence`) & !is.na(studytype))

>>>>

---
title             : "Supplemental Material for the manuscript  'TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'"
shorttitle        : "Supplements"
author:

  - name          : "Julia Prein"
    affiliation   : "1"
    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
    email         : "julia_prein@eva.mpg.de"

  - name          : "Manuel Bohn"
    affiliation   : "1,2"
  - name          : "Steven Kalinke"
    affiliation   : "1"
  - name          : "Daniel B. M. Haun"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
  - id            : "2"
    institution   : "Institute of Psychology, Leuphana University Lüneburg, Germany" 
floatsintext      : yes
bibliography      : ["../../references.bib"]
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---

@@

```{r sample}
testtrials <- readRDS(file = "../data/tango-testtrials.rds")
```

@@

```{r webcam_table}
webcam_models <- readRDS(file = "../saves/supplements_webcamcoding_results.rds") %>%
  mutate(across(c(WAIC, Weight, ELPD_DIFF, SE_ELPD_DIFF), as.numeric)) %>%
  mutate_if(is.numeric, round, 2)

@@

```{r adult_sample_country, include=FALSE}
levels(testtrials$currentResidence)
```

```{r adult_sample_countryn, echo=FALSE}
adult_sample_countryn <- testtrials %>% 
  group_by(subjID) %>% 
  slice(1) %>% 
  group_by(currentResidence, studytype) %>%
  summarise(n = n()) %>%
  arrange(studytype, -n) %>% 
  filter(!is.na(currentResidence) & !is.na(studytype))
